Merging merges, more or less

### 2015-03-02 2015mergingmerges/Main.tex
words
ok

\begin{abstract}
\end{abstract}

@@

\input{section/01-Introduction.tex}

>>>>

\begin{abstract}
Fusion is an essential part of optimising high-level array computations.
Fusion systems for combinators tend to focus on combinators with data-independent access patterns such as @zip@, @filter@ and @map@, while ignoring @merge@ as in merge sort.
In this paper, we show that describing combinators as deterministic finite automata allows us to express more combinators, while leading to a fusion algorithm based on intersection of automata.
\end{abstract}

@@

\input{section/01-Introduction.tex}
\input{section/02-Streams.tex}
\input{section/03-Access.tex}
\input{section/XX-RelatedWork.tex}

### 2015-03-02 2015mergingmerges/section/01-Introduction.tex
ok

Consider the following program, which partitions its input array by the first element of each pair.
If we plan on executing this program with data that is too large to execute in memory, what is the best execution strategy?

\begin{code}
app2 :: [(Bool,a)] -> [(Bool,a)]
app2 xs
  = filter     (fst) xs
 ++ filter (not.fst) xs

main
  = do xs  <- readMassiveFile
       sendEmails (app2 xs)
\end{code}

>>>>

Consider the following program, which loads some accounts, sums up the balance of their loans, and sends debt collection emails to some, while raises the credit card limit of others.
Can we execute this without buffering the entire file in memory? Perhaps not, but we could if the relative ordering of debt collecting and raising limits is not important.
If we plan on executing this program with data that is too large to execute in memory, what is the best execution strategy?

\begin{code}
arrearsOffers
    :: [(AccountId, Account)]
    -> [(AccountId, Loan)]
    -> ([Account], [Account])
arrearsOffers as ls
 = let als  = merge as ls
       bals = group_by sum_balance als
       arrs = filter (<0   . balance) bals
       offs = filter (>500 . balance) bals
   in (arrs, offs)

main
 = do accounts <- readAccounts
      loans    <- readLoans
      let (arrears, offers)
                = arrearsOffers accounts loans
      mapM_ sendDebtCollector arrears
      mapM_ raiseLimit        offers
\end{code}
